\documentclass[12pt]{article}

\usepackage{enumerate}
\usepackage[margin=0.5in]{geometry}
\usepackage{tikz}
\usepackage{hyperref}

\usepackage{color}
\newcommand{\todo}[1]{{\color{red}[[\textbf{XXX TODO: }#1]]}}
\newcommand{\response}[1]{{\color{blue}#1}}

%\newcommand{\yes}{\tikz \node[draw,circle]{Yes}; No\\ }
\newcommand{\yes}{{\color{blue}YES}\\ }
\newcommand{\no}{{\color{blue}NO}\\ }
\newcommand{\na}{{\color{blue}Not applicable} }
\newcommand{\yn}{{Yes~~~No\\ }}

\begin{document}

\title{\bf MONTANA STATE UNIVERSITY}
\author{\bf Request for Designation of Research as Exempt from the\\
    \bf Requirement of Institutional Review Board
}
\date{(2/1/2020)}

\maketitle

\begin{center}
    ***************************************************************************************
    \\
    \small
    THIS AREA IS FOR INSTITUTIONAL REVIEW BOARD USE ONLY. DO NOT WRITE IN THIS
    AREA.\\
    \vspace{1.75in}
    ***************************************************************************************
\end{center}

\noindent
{\bf DATE:} \response{\todo{date}}

\begin{enumerate}[I.]
    \item INVESTIGATOR(s):\\
        Name: \response{Brittany Terese Fasy}\\
        MSU Department: \response{Gianforte School of Computing}\\
        Telephone: \response{x4804}\\
        E-Mail Address: \response{brittany.fasy@montana.edu}\\
        DATE TRAINING COMPLETED: \response{19-Dec-2019} [Required training: CITI
        training; see website for link]\\
        Name of Faculty Sponser (if the above is a student; also must complete
        CITI training): \response{n/a}
        \\~\\
        SIGNATURE (INVESTIGATOR or ADVISOR):\rule{0.5\linewidth}{\linethickness}   \\

        (If more than one investigator, repeat information for all investigators
        or team members).

        Name: \response{David L.\ Millman}\\
        E-mail address: \response{david.millman@montana.edu}\\
        DATE TRAINING COMPLETED: \response{3 April 2019}\\

        Name: \todo{}\\
        MSU Department: \todo{}\\
        Telephone: \todo{}\\
        E-Mail Address: \todo{}\\
        DATE TRAINING COMPLETED: \todo{} [Required training: CITI
        training; see website for link]\\
        \\~\\
        SIGNATURE (INVESTIGATOR):\rule{0.5\linewidth}{\linethickness}   \\

        {\bf \color{red} \underline{Conflict of Interest Statement}}
        %
        Do the investigator(s) or other researchers involved in research design,
        conduct, or reporting (and their family members) have an outside
        interest related to the research?\\
        \todo{\yes or \no}

        If yes, please contact the Office of Research Compliance at
        406.994.6757 for further guidance.

    \item TITLE OF RESEARCH PROJECT:  (Try to keep title on first page.)
        \response{TODO}

    \item BRIEF DESCRIPTION OF RESEARCH METHODS (also see section VII).  If
        using a survey/questionnaire,
                  provide a copy with this application.
                  \response{TODO
                  }

    \item RISKS AND INCONVENIENCES TO SUBJECTS (also see section VII; do not
        answer {\bf `None'}): \response{TODO
        The main inconvenience of this survey is additional time required to complete
    the exit survey.}

    \item SUBJECTS:
        \begin{enumerate}[A.]
            \item Expected number of subjects: \response{TODO}
            \item Will research involve minors (age $<18$ years)?  \yes
                        (If `Yes', please specify and justify.)
                        \response{TODO}
            \item Will research involve prisoners? \no
            \item Will research involve any specific ethnic, racial,
                religious, etc.  groups of people? \no
                (If 'Yes', please specify and justify.)
            \item Will a consent form be used?  \yes
                (Please use accepted format
                from our website. Be sure to indicate that participation is
                voluntary. Provide a stand-alone copy. Do not include the form
                here.)
        \end{enumerate}

    \item FOR RESEARCH INVOLVING SURVEYS OR QUESTIONNAIRES:\\
            (Be sure to indicate on each instrument, survey or questionnaire
            that participation is voluntary.)
        \begin{enumerate}[A.]
                \item Is information being collected about:\\
                    Sexual behavior? \no
                    Criminal behavior? \no
                    Alcohol or substance abuse? \no
                    Matters affecting employment? \no
                    Matters relating to civil litigation? \no
                \item Will the information obtained be completely anonymous,
                    with no identifying information linked to the responding
                    subjects? \todo{}
                \item If identifying information will be linked to the
                    responding subjects, how will the subjects be identified?
                    (Please circle or bold your answers) \na \\
                    By name \todo{YES or NO}\\
                    By code \todo{YES or NO} \\
                    By other identifying information \todo{YES or NO}
                \item Does this survey utilize a standardized and/or
                    validated survey tool/questionnaire? \no
        \end{enumerate}

    \item FOR RESEARCH BEING CONDUCTED IN A CLASSROOM SETTING: \na

        \begin{enumerate}[A.]
            \item Will research involve blood draws?  (If Yes, please follow
                protocol listed in the “Guidelines for Describing Risks: blood,
                etc.”, section I-VI.) \no
        \end{enumerate}

    \item FOR RESEARCH INVOLVING PATIENT INFORMATION, MATERIALS, BLOOD OR TISSUE
            SPECIMENS RECEIVED FROM OTHER INSTITUTIONS: \na

            \begin{enumerate}[A.]
                \item Are these materials linked in any way to the patient
                    (code, identifier, or other link to
                            patient identity)? \yn
                \item Are you involved in the design of the study for which the
                    materials are being collected? \yn
                \item Will your name appear on publications resulting from this
                    research? \yn
                \item Where are the subjects from whom this material is being
                    collected?
                \item Has an IRB at the institution releasing this material
                    reviewed the proposed project? \yn
                                (If 'Yes", please provide documentation.)
                \item Regarding the above materials or data, will you be:\\
                    Collecting them \yn
                    Receiving them \yn
                    Sending them \yn

                \item Do the materials already exist? \yn

                \item Are the materials being collected for the purpose of this
                    study? \yn

                \item Do the materials come from subjects who are: \\
                    Minors \yn
                    Prisoners \yn
                    Pregnant women \yn

                \item J. Does this material originate from a patient population
                    that, for religious or other reasons,
                            would prohibit its use in biomedical research?
                            Yes No Unknown source

           \end{enumerate}

    \item FOR RESEARCH INVOLVING MEDICAL AND/OR INSURANCE RECORDS: \na

            \begin{enumerate}[A.]
                \item Does this research involve the use of: \\
                      Medical, psychiatric and/or psychological records \yn
                      Health insurance records   \yn
                      Any other records containing information regarding personal
                                            health and illness \yn

                If you answered `Yes' to any of the items in this section, you
                must complete the HIPAA Worksheet.
            \end{enumerate}

\end{enumerate}

\end{document}
