
\documentclass{article}

\usepackage{enumerate}
\usepackage[margin=0.5in]{geometry}
\usepackage{tikz}
\usepackage{hyperref}

\usepackage{color}
\newcommand{\todo}[1]{{\color{red}[[\textbf{XXX TODO: }#1]]}}
\newcommand{\response}[1]{{\color{blue}#1}}

%\newcommand{\yes}{\tikz \node[draw,circle]{Yes}; No\\ }
\newcommand{\yes}{{\color{blue}YES}\\ }
\newcommand{\no}{{\color{blue}NO}\\ }
\newcommand{\na}{{\color{blue}Not applicable} }
\newcommand{\yn}{{Yes~~~No\\ }}

\begin{document}

\title{\bf MONTANA STATE UNIVERSITY}
\author{\bf Institiutional Review Board Application for Review \\
    \bf revised 06/01/15
}
\date{}

\maketitle

\begin{center}
    ***************************************************************************************
    \\
    \small
    THIS AREA IS FOR INSTITUTIONAL REVIEW BOARD USE ONLY. DO NOT WRITE IN THIS
    AREA.\\
    \hspace{-4in} Application number:\\ \hspace{-4.25in}Approval Date:\\
    \hspace{-4.4in}  Disapproved:\\\hspace{-3.8in}IRB Chair's Signature:\\
    ***************************************************************************************
\end{center}

\noindent
{\bf DATE:} \response{TODO:date}

\begin{enumerate}[I.]

    \item INVESTIGATOR(s) AND ASSOCIATE(s):\\
        (list all invesotgators involved, application will be filed under name of first\\
        person listed)\\
        \\
        Name: \response{Brittany Terese Fasy}\\
        Title: \\
        Complete Department and/or Home address (where you want the approval
        letter sent):\\
            \response{
            Gianforte School of Computing\\
            357 Barnard Hall\\
            P.O. Box 173880\\
            Montana State University\\
            Bozeman, MT 59717-3880}\\
        E-Mail Address: \response{brittany.fasy@montana.edu}\\
        Phone: \response{x4804} \\
        DATE TRAINING COMPLETED: \response{19-Dec-2019} [Required training: CITI
        training; see website for link]\\


        SIGNATURE (INVESTIGATOR or ADVISOR):\rule{0.5\linewidth}{\linethickness}   \\

        (If more than one investigator, repeat information for all investigators
        or team members).

        Name: \\
        Title: \\
        Complete Department and/or Home address (where you want the approval
        letter sent):\\
            \\
        E-Mail Address: \\
        Phone: \\
        DATE TRAINING COMPLETED: [Required training: CITI
        training; see website for link]\\

        \textbf(repeat for additional investigators if needed; or delete extra if not necessarry)\\

        \color{red}
        Do you as PI, any family member or any of the involved researchers or their family members\\
        have consulting agreements, management resposnibilities or substantial equity (greater than\\
        10,000 dollars in valure or greater than 5 percent total equity) in the sponsor, subcontractor\\
        or in the technology, or servve on the Board of the Sponsor? Yes or No\\

        If you answered yes, you will need to contact Kellie Peterson, Legal Counsel-JD at 406-994-3480
        \color{black}


    \item TITLE OF PROPOSAL:  (Try to keep title on first page.)
        \response{TODO}

    \item BEGINNING DATE OF USE FOR HUMAN SUBJECTS: \response{TODO}

    \item TYPE OF GRANT AND/OR PROJECT (if applicable)\\
    Research Grant:\response{TODO} \\
    Contract: \response{TODO} \\
    Training Grant: \response{TODO} \\
    Classroom Experiments/Projects:\response{TODO} \\
    Thesis Project: \response{TODO} \\
    Other (Specify): \response{TODO} \\

    \item NAME OF FUNDING AGENCY TO WHICH PROPOSAL IS BEING SUBMITTED (if applicable): \response{TODO}

    \item SIGNATURES:\\
    \textbf{Submitted by Investigator}\\
    Typed Name: \response{TODO} \\
    Signature: \response{TODO} \\
    Date: \response{TODO} \\
    \textbf{Faculty Sponsor (for student)}\\
    Typed Name: \response{TODO} \\
    Siganture: \response{TODO} \\
    Date: \response{TODO} \\

    \item SUMMARY OF ACTIVITY: Provide answers to each section and add spaces as needed. Do not refer to an \\
    accompanying grant or contract proposal.
    \begin{enumerate}[A.]
        \item RATIONALE AND PURPOSE OF RESEARCH (What question is being asked?)

        \response{TODO}

        \item RESEARCH PROCEDURES INVOLVED Provide a short description of sequence and methods of procedures \\
        that will be performed with the human subjects. Inlude details of painful or uncomfortable procedures, \\
        frequency of procedures, time involved, names of psychological tests, questionnaires, restrictions on \\
        usual life patterns, and follow up procedures. \color{red} \emph{If you are planning on posting flyers, posters, ets. anywhere on \\
        campus, you must check with the building managers and/or departments located in MSU\\
        buildings and obtain their approval prior to the posting.}\\\color{black}

        \response{TODO}

        \item DECEPTION - If any deception (withholding of complete information) is required for the validity of this\\
        activty, explain why this is necessarry and attach debriefing statement. \\

        \response{TODO}

        \item SUBJECTS
        \begin{enumerate}[1.]

            \item Approximate number and ages
            How Many Subjects: \response{TODO} \\
            Age Range of Subjects: \response{TODO} \\
            How Many Normal/Control: \response{TODO} \\
            Age Range of Normal/Control: \response{TODO} \\

            \item Criteria for selection: \response{TODO} \\

            \item Criteria for exclusion: \response{TODO} \\

            \item Source of Subjects (including patients): \response{TODO} \\

            \item Who will approach subects and how? Explain steps take to avoid coercion. \response{TODO} \\

            \item Will subjects receive payments, service without charge, or
                extra course credit? \yn
            (If yes, what amount and how? Are there other ways to receive similar benefits?) \response{TODO} \\

            \item Location(s) where procedures will be carried out. \response{TODO} \\
        \end{enumerate}

        \item RISKS AND BENEFITS (ADVERSE EFFECTS)
        \begin{enumerate}[1.]
            \item Describe nature and amount of risk and/or adverse effects (include side effects), substantial stress,\\
            discomfort, or invasion of prrivacy involved. \response{TODO} \\

            \item Will this study preclude standard procedures (e.g., medical or psychological care, school attendace, etc.)?\\
            If yes, explain. \response{TODO} \\

            \item Describe the expected benefits for individual subjects and/or society. \response{TODO} \\

        \end{enumerate}
        \item ADVERSE EFFECTS
        \begin{enumerate}[1.]
            \item How will possible adverse effects be handled? \response{TODO} \\
            By investogator(s):
            Referred by investogator(s) to appropriate care:
            Other (explain):\\

            \item Are facilities/equipment adequate to handle possible adverse
                effects? \yn
            (If no, explain) \response{TODO}\\

            \item Describe arrangements for financial responsibility for any possible adverse effects.\\
            MSU Compensation(explain): \\
            Sponsoring agency insurance: \\
            Subject is responsible: \\
            Other (explain): response{TODO}\\

        \end{enumerate}
        \item CONFIDENTIALITY OF RESEARCH DATA\\

        \begin{enumerate}[1.]
            \item Will data be coded? \yn \\

            \item Will master code be kept separate from data? \yn \\

            \item Will any other agency have access to identifiable data? \yn \\

            \item How will documents, data be stored and protected?
                \response{TODO} \\
            Locked file:\\
            Computer with restricted password:\\
            Other(explain):\\

        \end{enumerate}
    \end{enumerate}
    \item CHECKLIST TO BE COMPLETED BY INVESTIGATOR(s):

    \begin{enumerate}[A.]
        \item Will any group, agency or organization be involved? \yn \\
        (If yes, please confirm that appropriate permissions have been obtained.)
            \response{TODO}

        \item Will materials with potential radiation risk be used (e.g. x-rays,
            radioisotopes)? \yn

        \begin{enumerate}[1.]
            \item Status of annual review but MSU Radiation Sources Committee(RSC). Pending or Approved \\
                (If approved, attach one copy of approval notice)
                \response{TODO}

            \item Title of application submitted to MSU RSC (if different). \response{TODO}

        \end{enumerate}
        \item Will human blood be utilized in your proposal? \no \\
        (If yes, please answer the following)

        \begin{enumerate}[1.]
            \item Will blood be drawn? \yn \\
            (If yes, who will draw the blood and how is the individual qualified to draw blood? \\
            What procdedure will be utilized?)\\

            \item Will the blood be tested for HIV? \yn \\

            \item What disposition will be made of unused blood? \\

            \item Has the MSU Occupational Health Officer been contacted? \yn \\

        \end{enumerate}

        \item Will non-investigational drugs or other substances be used for
            purposes of the research? \no \\

        Name:\\
        Dose:\\
        Source:\\
        How Administered:\\
        Side effects:\\

        \item Will any investigational new drugs or other investigational
            substances be used? \no \\
        (If yes, provide information requested below and one copy of: 1) available toxicity data; 2) reports of animal studies;\\
        3) description of studies done in humans; 4) concise review of the literature prepared by the investigators(s); \\
        and 5) the drug protocol)\\

        Name:\\
        Dose: \\
        Source: \\
        How Administered: \\
        IND Number: \\
        Phase of Testing: \\

        \item Will an investigation device be used? \yn \\
        (If yes, provide a name, source description of purpose, how used, and status with the U.S. Food and Drug \\
        Administration FDA. Include a statement as to whether or not device poses a significant risk. Attach any \\
        relevant material.)

        \item Will academic records be used? \yn

        \item Will this research involve the use of:
        Medical, phsychiatric and/or phsychological records \yn \\
        Health insurance records \yn \\
        Any other records containing information regarding personal health and
        illness \yn \\

        If you answered "Yes" to any of the items under "H.", you must complete the \textbf{HIPAA worskeet.}\\

        \item Will audio-visual or tape recordings or photographs be made? \yn

        \item Will written consent form(s) be used? (\yn . If no, explain.) (Please use accepted format from \\
        our website. Be sure to indicate that participation is voluntary. Provide a stand-alone copy; do not \\
        include the form here.)


    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{enumerate}

\end{document}
